A meta-analysis of mental rotation ability in the first years of life

### 2022-04-08 code/analysis.Rmd
Update figure size
Funnel plots

# Global chunk options
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

@@

# Three-level model
res_mv <- rma.mv(
  yi, vi,
  random = ~ group | id,
  data = dat_r,
  slab = experiment_ids
)
print(res_mv)
forest(res_mv)

@@

# Meta-regression with gender
res_gender <- rma.mv(
  yi, vi,
  mods = ~female_percent,
  random = ~ group | id,
  data = dat_r,
  slab = experiment_ids
)
print(res_gender)
forest(res_gender)

# Meta-regression with age, gender, and their interaction
res_full <- rma.mv(
  yi, vi,
  mods = ~ age_months * female_percent,
  random = ~ group | id,
  data = dat_r,
  slab = experiment_ids
)
print(res_full)
forest(res_full)
```

>>>>

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  fig.height = 10,
  fig.width = 7.5,
  out.width = "100%"
)
```

@@

# Three-level model
res_mv <- rma.mv(
  yi, vi,
  random = ~ group | id,
  data = dat_r,
  slab = experiment_ids
)
print(res_mv)
forest(res_mv)
funnel(res_mv, main = "Standard Error")

@@

# Meta-regression with gender
res_gender <- rma.mv(
  yi, vi,
  mods = ~female_percent,
  random = ~ group | id,
  data = dat_r,
  slab = experiment_ids
)
print(res_gender)
forest(res_gender)
funnel(res_age, main = "Standard Error")

# Meta-regression with age, gender, and their interaction
res_full <- rma.mv(
  yi, vi,
  mods = ~ age_months * female_percent,
  random = ~ group | id,
  data = dat_r,
  slab = experiment_ids
)
print(res_full)
forest(res_full)
funnel(res_full, main = "Standard Error")
```
